Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2012-08-15 paper.tex
Added to paper.  Need the covering lemma now.

Put 
\[
f_i(\lambda, R_i, \Phi_i) = \begin{cases}
R_i( \sin(\lambda + \Phi_i) - \sin(\Phi_i)), & i \in P \\
R_i( \sin\sfracpart{\lambda + \Phi_i} - \sin\sfracpart{\Phi_i}), & i \in D \\
\end{cases}
\]
so that
\[
W_L(\lambda) = \frac{1}{\sqrt{L}} \sum_{i \in P \cup D} \big( f_i(\lambda, R_i, \Phi_i) - \expect f_i(\lambda, R_i, \Phi_i) \big).
\]
Let $\{g_i\}$ be a sequence of independent standard normal random variables, independent of $\{R_i\}$ and $\{\Phi_i\}$.  Lemma~\ref{lem:symmetrisation} shows that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq \sqrt{2\pi} \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ X_L(\lambda) },
\]
where 
\begin{equation}\label{eq:ZpsiCondGaussProc}
X_L(\lambda) = \frac{1}{\sqrt{L}} \sum_{i \in P \cup D} g_i f_i(\lambda, R_i, \Phi_i),
\end{equation}
and where $\expect$ runs over all of $\{g_i\}$, $\{R_i\}$ and $\{\Phi_i\}$.  Conditionally on $\{\Phi_i\}$ and $\{R_i\}$, $\{X_L(\lambda), \lambda \in \reals \}$ is a \emph{Gaussian process}, and numerous techniques exist for its analysis.  Lemma~\ref{lem:chaining} shows that for any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\lambda) } < \kappa.
\]
It follows that,
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)}  <  \sqrt{2\pi} \; \kappa,
\]
and by Markov's inequality,
\[
\prob \cubr{  \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} > \delta } \leq  \sqrt{2\pi} \; \frac{\kappa}{\delta},
\]
for any $\delta > 0$.  The proof follows by choosing $\nu =  \sqrt{2\pi} \kappa/\delta$.  It remains to prove Lemmas~\ref{lem:symmetrisation}~and~\ref{lem:chaining}.
\end{IEEEproof}

@@

\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq \sqrt{2\pi} \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ X_L(\lambda) }

@@

By the triangle inequality

@@

&= \sqrt{2\pi} \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ X_L(\lambda) } 

@@

\begin{lemma} \label{lem:chaining}
For any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\lambda) } < \kappa,
\]
where $X_L(\lambda)$ is defined in~\eqref{eq:ZpsiCondGaussProc}.
\end{lemma}
\begin{IEEEproof}
Without loss of generality, assume that $\epsilon < \tfrac{\pi}{M}$.  Lemma~\ref{lem:chaining2} shows that
\begin{equation}\label{eq:supZCK1} 
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\psibf) } \leq K_1 \sqrt{\frac{C_\epsilon}{L}}
\end{equation}
where $K_1$ is a finite, positive constant, and
\[
C_\epsilon = 2\epsilon\sum_{i\in P \cup D}R_i^2 + 4\sum_{i\in P \cup D}R_i^2 I_{\epsilon}(\Phi_i)
\]
where $I_{\epsilon}(\Phi_i)$ returns one when $\Phi_i \in \cup_{k\in\ints}[\psi_k - \epsilon, \psi_k + \epsilon]$ and zero otherwise.  Now,
\[
\tfrac{1}{L}\expect C_\epsilon =  2\epsilon\expect R_1^2 + 4 \expect R_i^2 I_{\epsilon}(\Phi_i).
\]
Recalling that $f(r,\phi)$ is the joint probability density function of $R_i$ and $\Phi_i$,
\begin{align*}
\expect R_i^2 I_\epsilon(\Phi_i) &= \int_0^{2\pi} \int_{0}^\infty  r^2 f(r,\phi) I_\epsilon(\phi) dr d\phi \\ 
&= \int_0^{2\pi}g_2(\phi) I_\epsilon(\phi) d\phi 
\end{align*}
where the function 
\[
g_2(\phi) = \int_{0}^\infty  r^2 f(r,\phi) dr d\phi 
\]
is continuous due to Lemma~\ref{lem:gg2cont}.  From the definition of $I_\epsilon$,
\begin{align*}
\expect R_i^2 I_\epsilon(\Phi_i) &= \sum_{k=0}^{M-1}\int_{\psi_k-\epsilon}^{\psi_k-\epsilon}g_2(\phi) d\phi \\
&= 2\epsilon \sum_{k=0}^{M-1} (g_2(\psi_k) + o(1))
\end{align*}
where $o(1)$ goes to zero as $\epsilon$ goes to zero, by the mean value theorem.  Thus $\expect R_i^2 I_\epsilon(\Phi_i) \leq K_2\epsilon$ for some constant $K_2$. Since $\sqrt{\cdot}$ is a concave function on the positive real line, and since $C_{\epsilon}$ is always positive, then
\[
\expect \sqrt{\frac{C_\epsilon}{L}} \leq  \sqrt{\tfrac{1}{L}\expect  C_\epsilon} < \sqrt{\epsilon( K_2 + 2\expect R_1^2)  }
\]
by Jensen's inequality.  Applying $\expect$ to both sides of~\eqref{eq:supZCK1},
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\psibf) } \leq K_1 \sqrt{\tfrac{1}{L}\expect C_\epsilon} < K_1 \sqrt{\epsilon( K_2 + 2\expect R_1^2)}.
\]
Choosing 
\[
\epsilon = \frac{\kappa^2}{ K_1^2 ( K_2 + 2\expect R_1^2)}
\] 
completes the proof.  It remains to prove Lemma~\ref{lem:chaining2}.
\end{IEEEproof}

The proofs of Lemmas~\ref{lem:chaining2}~and~\ref{lem:chaining3} are based on a technique called \emph{chaining} (or \emph{bracketing})~\cite{Dudley_unif_central_lim_th_1999,Ossiander_clt_bracketing_1984,Pollard_asymp_empi_proc_1989,Pollard_new_ways_clts_1986}.  The proofs here follow those of Pollard~\cite[Section 3]{Pollard_asymp_empi_proc_1989}.  %Within the remaining proofs, we are interested in expectations conditional on the phase noise sequence $\{\Phi_n\}$, so for the purpose of these lemmas, $\{\Phi_n\}$ is treated as a fixed realisation.  
For notational convenience we use the abbreviation 
\[
f_{i}(\lambda) = f_{i}(\lambda, R_i, \Phi_i)
\]
in what follows.  As in Lemma~\ref{lem:chaining} we assume, without loss of generality, that $\epsilon < \tfrac{1}{m+1}$.  %This comes at no loss since Lemma~\ref{lem:chaining} only asks for the existence of an $\epsilon > 0$.

\begin{lemma}\label{lem:chaining2}
There exists a positive constant $K_1$ such that
\[
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\lambda) } \leq K_1 \sqrt{\frac{C_\epsilon}{L}}.
\]
\end{lemma}
\begin{IEEEproof}
Let $B_\epsilon = \{x \in \reals \mid \abs{x} < \epsilon\}$ be the set of real numbers with magnitude less than $\epsilon$.  For each non negative integer $k$, let $T_\epsilon(k)$ be a discrete subset of $B_\epsilon$ with the property that for every $\lambda \in B_\epsilon$ there exists $\lambda_1$ and $\lambda_2$ in $T_\epsilon(k)$ such that the psuedometric
\[
d_1(\lambda, \lambda_1) = \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda_1) \big)^2 \leq 2^{-k} C_\epsilon,
\]
and the psuedometric
\[
d_2(\lambda, \lambda_2) = \sum_{i \in P \cup D} \sabs{f_{i}(\lambda) - f_{i}(\lambda_2)} \leq 2^{-k} D_\epsilon
\]
where 
\[
D_\epsilon = \epsilon\sum_{i\in P \cup D}R_i + \sum_{i\in P \cup D}R_i I_{\epsilon}(\Phi_i).
\]
We specifically define $T_\epsilon(0)$ to contain only zero.  Defined this way, $T_\epsilon(0)$ satisfies the inequality above because both $d_1(\lambda, 0)$ and $d_2(\lambda, 0)$ are less than $C_\epsilon$ for all $\lambda \in B_\epsilon$, as a result of Lemma~\ref{lem:epslmlemma}.  The existance of $T_\epsilon(k)$ for every positive integer $k$ will be proved by construction in Lemma~\ref{}.

Lemma~\ref{lem:limexpTk} shows that
\[
\lim_{k\rightarrow\infty}\expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k)} \sabs{X_L(\lambda)} = \expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \sabs{X_L(\lambda)}.
\]
Lemma~\ref{lem:chaining3} shows that
\[
\expect_{R,\Phi} \sup_{\lambda \in T_\epsilon(k)} \sabs{X_L(\lambda)} \leq \sqrt{\frac{C_\epsilon}{L}} \sum_{i=1}^{k} \frac{?}{2^{i/2}}
\]
The sum above converges as $k\rightarrow\infty$ so lemma holds with
\[
K_1 = \sum_{i=1}^{\infty} \frac{?}{2^{i/2}}.
\]
\end{IEEEproof}

\begin{lemma}\label{lem:limexpTk}
\[
\lim_{k\rightarrow\infty}\expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k)} \sabs{X_L(\lambda)} = \expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \sabs{X_L(\lambda)}
\]
\end{lemma}
\begin{IEEEproof}
Because $T_\epsilon(k)$ is a subset of $B_\epsilon$,
\[
\sup_{\lambda \in T_\epsilon(k)} \sabs{X_L(\lambda)} \leq \sup_{\sabs{\lambda} < \epsilon} \sabs{X_L(\lambda)}.
\]
Let $\lambda^* \in B_\epsilon$ be a maximiser of $\sabs{X_L(\lambda)}$, that is
\[
\sabs{X_L(\lambda^*)} = \sup_{\sabs{\lambda} < \epsilon}\sabs{X_L(\lambda)}.
\]
By definition $T_\epsilon(k)$ contains a point $\lambda_2$ such that $d_2(\lambda^*,\lambda_2) \leq 2^{-k}D_\epsilon$.  Now
\begin{align*}
\sabs{X_L(\lambda^*) - X_L(\lambda_2)} &= \abs{\frac{1}{\sqrt{L}}\sum_{i\in P \cup D}g_i(f_i(\lambda^*) - f_i(\lambda_2))} \\
&\leq  \frac{1}{\sqrt{L}}\sum_{i\in P \cup D}\abs{g_i}\sabs{f_i(\lambda^*) - f_i(\lambda_2)} \\
&\leq \frac{g_\text{max}}{\sqrt{L}} \sum_{i\in P \cup D}\sabs{f_i(\lambda^*) - f_i(\lambda_2)} \\
&\leq \frac{g_\text{max}}{\sqrt{L}} d(\lambda^*,\lambda_2) \\
&\leq \frac{g_\text{max}}{\sqrt{L}} 2^{-k} D_\epsilon.
\end{align*}
where $g_\text{max} = \max_{i\in P\cup D} \abs{g_i}$.
\end{IEEEproof}

\begin{lemma}\label{lem:epslmlemma}
Suppose $\sabs{\lambda} < \epsilon$ and $\sabs{\lambda^*} < \epsilon$ with $\epsilon < \tfrac{\pi}{M}$. Then
\begin{align*}
d(\lambda, \lambda^*) &= \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda^*) \big)^2 \\
&\leq R_i^2 L \left( (\lambda - \lambda^*)^2 + 4 C_\epsilon \right).
\end{align*}
\end{lemma}

\begin{lemma}
If $i \in P$, then $\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 \leq R_i^2(\lambda - \lambda^*)^2.$
\end{lemma}
\begin{IEEEproof} 
We have
\[
\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 = R_i^2\sabs{\sin(\lambda + \Phi_i) - \sin(\lambda^* + \Phi_i)}^2
\]
and, since $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
\[
\sabs{\sin(\lambda + \Phi_i) - \sin(\lambda^* + \Phi_i)} \leq K\sabs{\lambda - \lambda^*} = \sabs{\lambda - \lambda^*}.
\]
\end{IEEEproof}

\begin{lemma}
Suppose $\sabs{\lambda} < \epsilon$ and $\sabs{\lambda^*} < \epsilon$ with $\epsilon < \tfrac{\pi}{M}$.  If $i \in D$, then
\begin{equation}\label{eq:fismall}
\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 \leq R_i^2(\lambda - \lambda^*)^2
\end{equation}
when $\Phi_i \notin S_\epsilon$, otherwise,
\begin{equation}\label{eq:fibig}
\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 \leq 4 R_i^2.
\end{equation}
\end{lemma}
\begin{IEEEproof}
Because $\sin(\cdot) \leq 1$ it follows that
\begin{align*}
\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 &= R_i^2\sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\lambda^* + \Phi_i}}^2 \\
&\leq 4 R_i^2
\end{align*}
for any $\Phi_i \in \reals$, and so~\eqref{eq:fibig} holds.  If $\Phi_i \notin S_\epsilon$ then $\Phi_i \in (\psi_{k-1} + \epsilon, \psi_{k} - \epsilon)$ for some $k\in\ints$ and 
\[
\fracpart{\Phi_i + \lambda} = \Phi_i + \lambda - \tfrac{2\pi}{M}k
\] 
and
\[
\fracpart{\Phi_i + \lambda^*} = \Phi_i + \lambda^* - \tfrac{2\pi}{M}k 
\]
and, since $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
\begin{align*}
\vert \sin&\fracpart{\Phi_i + \lambda} - \sin\fracpart{\Phi_i + \lambda^*}\vert \\
&=  \sabs{\sin(\Phi_i + \lambda - \tfrac{2\pi}{M}k) - \sin(\Phi_i + \lambda^* - \tfrac{2\pi}{M}k)} \\
&\leq K \sabs{\lambda - \lambda^*} \\
&= \sabs{\lambda - \lambda^*}.
\end{align*}
Thus~\eqref{eq:fismall} holds. 
\end{IEEEproof}

\begin{lemma}\label{lem:chaining3}(Chaining)
For all positive integers $k$,
\[
\expect_{R,\Phi} \sup_{\psibf \in T_\epsilon(k) } \abs{ X_L(\lambda) } \leq \sqrt{C_\epsilon} \sum_{i=1}^{k}\frac{?}{2^{i/2}}.
\]
\end{lemma}
\begin{IEEEproof}
Let $b_k(\lambda)$ maps each $\lambda \in T_\epsilon(k)$ to an element in $T_\epsilon(k-1)$ such that 
\[
d(\lambda, b_k(\lambda)) \leq 2^{1-k}C_\epsilon.
\]
The existance of $b_k$ is guaranteed by the definition of $T_\epsilon(k-1)$. 
\end{IEEEproof}

>>>>

Put 
\[
f_i(\lambda, R_i, \Phi_i) = \begin{cases}
R_i( \sin(\lambda + \Phi_i) - \sin(\Phi_i)), & i \in P \\
R_i( \sin\sfracpart{\lambda + \Phi_i} - \sin\sfracpart{\Phi_i}), & i \in D \\
\end{cases}
\]
so that
\[
W_L(\lambda) = \frac{1}{\sqrt{L}} \sum_{i \in P \cup D} \big( f_i(\lambda, R_i, \Phi_i) - \expect f_i(\lambda, R_i, \Phi_i) \big).
\]
Let $\{g_i\}$ be a sequence of independent standard normal random variables, independent of $\{R_i\}$ and $\{\Phi_i\}$.  Lemma~\ref{lem:symmetrisation} shows that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq \sqrt{2\pi} \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ X(\lambda) },
\]
where 
\begin{equation}\label{eq:ZpsiCondGaussProc}
X(\lambda) = \frac{1}{\sqrt{L}} \sum_{i \in P \cup D} g_i f_i(\lambda, R_i, \Phi_i),
\end{equation}
and where $\expect$ runs over all of $\{g_i\}$, $\{R_i\}$ and $\{\Phi_i\}$.  Conditionally on $\{\Phi_i\}$ and $\{R_i\}$, $\{X(\lambda), \lambda \in \reals \}$ is a \emph{Gaussian process}, and numerous techniques exist for its analysis.  Lemma~\ref{lem:chaining} shows that for any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } < \kappa.
\]
It follows that,
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)}  <  \sqrt{2\pi} \; \kappa,
\]
and by Markov's inequality,
\[
\prob \cubr{  \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} > \delta } \leq  \sqrt{2\pi} \; \frac{\kappa}{\delta},
\]
for any $\delta > 0$.  The proof follows by choosing $\nu =  \sqrt{2\pi} \kappa/\delta$.  It remains to prove Lemmas~\ref{lem:symmetrisation}~and~\ref{lem:chaining}.
\end{IEEEproof}

@@

\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq \sqrt{2\pi} \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ X(\lambda) }

@@

By the triangle inequality,

@@

&= \sqrt{2\pi} \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ X(\lambda) } 

@@

\begin{lemma} \label{lem:chaining}
For any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } < \kappa,
\]
where $X(\lambda)$ is the Gaussian process defined in~\eqref{eq:ZpsiCondGaussProc}.
\end{lemma}
\begin{IEEEproof}
Without loss of generality, assume that $\epsilon < \tfrac{\pi}{M}$.  Lemma~\ref{lem:chaining2} shows that
\begin{equation}\label{eq:supZCK1} 
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } \leq K_1 \sqrt{C_\epsilon}
\end{equation}
where $K_1$ is a finite, positive constant, and
\begin{equation}\label{eq:Cepsdefn}
C_\epsilon = \frac{2}{L}\epsilon\sum_{i\in P \cup D}R_i^2 + \frac{4}{L}\sum_{i\in P \cup D}R_i^2 I_{\epsilon}(\Phi_i)
\end{equation}
where $I_\epsilon$ is the indicator function
\[
I_{\epsilon}(x) = \begin{cases}
1, & x \in \cup_{k\in\ints}[\psi_k - \epsilon, \psi_k + \epsilon] \\
0, & \text{otherwise},
\end{cases}
\] 
and $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$.  Now,
\[
\expect C_\epsilon =  2\epsilon\expect R_1^2 + 4 \expect R_i^2 I_{\epsilon}(\Phi_i).
\]
Recalling that $f(r,\phi)$ is the joint probability density function of $R_i$ and $\Phi_i$,
\begin{align*}
\expect R_i^2 I_\epsilon(\Phi_i) &= \int_0^{2\pi} \int_{0}^\infty  r^2 f(r,\phi) I_\epsilon(\phi) dr d\phi \\ 
&= \int_0^{2\pi}g_2(\phi) I_\epsilon(\phi) d\phi 
\end{align*}
where the function
\[
g_2(\phi) = \int_{0}^\infty  r^2 f(r,\phi) dr d\phi 
\]
is continuous due to Lemma~\ref{lem:gg2cont}.  From the definition of $I_\epsilon$,
\begin{align*}
\expect R_i^2 I_\epsilon(\Phi_i) &= \sum_{k=0}^{M-1}\int_{\psi_k-\epsilon}^{\psi_k-\epsilon}g_2(\phi) d\phi \\
&= 2\epsilon \sum_{k=0}^{M-1} (g_2(\psi_k) + o(1))
\end{align*}
where $o(1)$ goes to zero as $\epsilon$ goes to zero, by the mean value theorem.  Thus $\expect R_i^2 I_\epsilon(\Phi_i) \leq K_2\epsilon$ for some constant $K_2$. Since $\sqrt{\cdot}$ is a concave function on the positive real line, and since $C_{\epsilon}$ is always positive, it follows that
\[
\expect \sqrt{C_\epsilon} \leq  \sqrt{\expect  C_\epsilon} < \sqrt{\epsilon( K_2 + 2\expect R_1^2)  }
\]
by Jensen's inequality.  Applying $\expect$ to both sides of~\eqref{eq:supZCK1},
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } \leq K_1 \sqrt{\tfrac{1}{L}\expect C_\epsilon} < K_1 \sqrt{\epsilon( K_2 + 2\expect R_1^2)}.
\]
Choosing 
\[
\epsilon = \frac{\kappa^2}{ K_1^2 ( K_2 + 2\expect R_1^2)}
\] 
completes the proof.  It remains to prove Lemma~\ref{lem:chaining2}.
\end{IEEEproof}

The proofs of Lemmas~\ref{lem:chaining2}~and~\ref{lem:chaining3} are based on a technique called \emph{chaining} (or \emph{bracketing})~\cite{Dudley_unif_central_lim_th_1999,Ossiander_clt_bracketing_1984,Pollard_asymp_empi_proc_1989,Pollard_new_ways_clts_1986}.  The proofs here follow those of Pollard~\cite[Section 3]{Pollard_asymp_empi_proc_1989}.  %Within the remaining proofs, we are interested in expectations conditional on the phase noise sequence $\{\Phi_n\}$, so for the purpose of these lemmas, $\{\Phi_n\}$ is treated as a fixed realisation.  
For notational convenience we use the abbreviation 
\[
f_{i}(\lambda) = f_{i}(\lambda, R_i, \Phi_i)
\]
in what follows.  As in Lemma~\ref{lem:chaining} we assume, without loss of generality, that $\epsilon < \tfrac{\pi}{M}$.  %This comes at no loss since Lemma~\ref{lem:chaining} only asks for the existence of an $\epsilon > 0$.

\begin{lemma}\label{lem:chaining2}
There exists a positive constant $K_1$ such that
\[
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } \leq K_1 \sqrt{C_\epsilon}.
\]
where $C_\epsilon$ is defined in~\eqref{eq:Cepsdefn}
\end{lemma}
\begin{IEEEproof}
Let $B_\epsilon = \{x \in \reals \mid \abs{x} < \epsilon\}$ be the set of real numbers with magnitude less than $\epsilon$.  For each non negative integer $k$, let $T_\epsilon(k)$ be a discrete subset of $B_\epsilon$ with the property that for every $\lambda \in B_\epsilon$ there exists $\lambda_1$ and $\lambda_2$ in $T_\epsilon(k)$ such that the psuedometric
\[
d_1(\lambda, \lambda_1) = \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda_1) \big)^2 \leq 2^{-k} C_\epsilon L,
\]
and the psuedometric
\[
d_2(\lambda, \lambda_2) = \sum_{i \in P \cup D} \sabs{f_{i}(\lambda) - f_{i}(\lambda_2)} \leq 2^{-k} D_\epsilon L
\]
where 
\begin{equation}\label{eq:Depsdefn}
D_\epsilon = \frac{1}{L}\epsilon\sum_{i\in P \cup D}R_i + \frac{1}{L}\sum_{i\in P \cup D}R_i I_{\epsilon}(\Phi_i).
\end{equation}
We specifically define $T_\epsilon(0)$ to contain only zero.  Defined this way, $T_\epsilon(0)$ satisfies the inequality above because $d_1(\lambda, 0) \leq C_\epsilon L $ and $d_2(\lambda, 0) \leq D_\epsilon L$ for all $\lambda \in B_\epsilon$, as a result of Lemma~\ref{lem:epslmlemma}.  The existance of $T_\epsilon(k)$ for every positive integer $k$ will be proved by construction in Lemma~\ref{lem:metricentropy}.  Lemma~\ref{lem:metricentropy} also shows that the number of elements in $T_\epsilon(k)$ is no more that $K_3 2^k$ where $K_3$ is a constant, independent of $L$, $\epsilon$ and $k$.

Lemma~\ref{lem:limexpTk} shows that
\[
\lim_{k\rightarrow\infty}\expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k)} \sabs{X(\lambda)} = \expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda)}.
\]
Lemma~\ref{lem:chaining3} shows that
\[
\expect_{R,\Phi} \sup_{\lambda \in T_\epsilon(k)} \sabs{X(\lambda)} \leq \sqrt{C_\epsilon} \sum_{i=1}^k \frac{5\sqrt{i \log 2 + \log K_3}}{2^{i/2}}
\]
The sum above converges as $k\rightarrow\infty$ so lemma holds with
\[
K_1 = \sum_{i=1}^\infty \frac{5\sqrt{i \log 2 + \log K_3}}{2^{i/2}}
\]
\end{IEEEproof}

\begin{lemma}
Both $d_1(\lambda, 0) \leq C_\epsilon L $ and $d_2(\lambda, 0) \leq D_\epsilon L$ for all $\lambda \in B_\epsilon$.
\end{lemma}
\begin{IEEEproof}
BLERG
\end{IEEEproof}

\begin{lemma}\label{lem:limexpTk} With $T_\epsilon(k)$ defined as in Lemma~\ref{lem:chaining2},
\[
\lim_{k\rightarrow\infty}\expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k)} \sabs{X(\lambda)} = \expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda)}
\]
\end{lemma}
\begin{IEEEproof}
Let $b_2(\lambda)$ be a function that maps $\lambda \in B_\epsilon$ to a point in $T_\epsilon(k)$ such that  $d_2(\lambda,b_2(\lambda)) \leq 2^{-k}D_\epsilon L$.  The existance of $b_2$ is guaranteed by the definition of $T_\epsilon(k-1)$.  So, for all $\lambda \in B_\epsilon$,
\begin{align*}
\sabs{X(\lambda) - X(b_2(\lambda))} &= \abs{\frac{1}{\sqrt{L}}\sum_{i\in P \cup D}g_i(f_i(\lambda) - f_i(b_2(\lambda)))} \\
&\leq  \frac{1}{\sqrt{L}}\sum_{i\in P \cup D}\abs{g_i}\sabs{f_i(\lambda) - f_i(b_2(\lambda))} \\
&\leq \frac{g_\text{max}}{\sqrt{L}} \sum_{i\in P \cup D}\sabs{f_i(\lambda) - f_i(b_2(\lambda))} \\
&\leq \frac{g_\text{max}}{\sqrt{L}} d_2(\lambda,b_2(\lambda)) \\
&\leq \frac{g_\text{max}}{\sqrt{L}} 2^{-k} D_\epsilon L,
\end{align*}
where $g_\text{max} = \max_{i\in P\cup D} \abs{g_i}$. The bound applies uniformly over $\lambda \in B_\epsilon$, so
\[
\sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda) - X(b_2(\lambda))} \leq \frac{g_\text{max}}{\sqrt{L}} 2^{-k} D_\epsilon L.
\]
Applying $\expect_{R,\Phi}$ to both sides of this inequality,
\[
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda) - X(b_2(\lambda))} \leq K_4 2^{-k} D_\epsilon L,
\]
where, as a result of Lemma~\ref{lem:maxineq},
\[
K_4 = \tfrac{1}{\sqrt{L}}\expect_{R,\Phi} g_\text{max} \leq 3 \sqrt{\frac{\log L}{L}}
\]
is a constant, independent of $\epsilon$ and $k$.  Because $T_\epsilon(k)$ is a subset of $B_\epsilon$,
\[
\sup_{\lambda \in T_\epsilon(k)} \expect_{R,\Phi} \sabs{X(\lambda)} \leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda)},
\]
and so,
\begin{align}
0 &\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda)} - \sup_{\lambda \in T_\epsilon(k)} \expect_{R,\Phi} \sabs{X(\lambda)} \nonumber \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda)} - \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(b_2(\lambda))} \nonumber \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \big( \sabs{X(\lambda)} - \sabs{X(b_2(\lambda))} \big) \nonumber \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda) - X(b_2(\lambda))} \nonumber \\
&\leq K_4 2^{-k} D_\epsilon L, \label{eq:Deps2nktozero}
\end{align}
the second line because,
\[
\sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(b_2(\lambda))} \leq \sup_{\lambda \in T_\epsilon(k)} \expect_{R,\Phi} \sabs{X(\lambda)},
\]
since $b_2(\lambda) \in T_\epsilon(k)$.  The lemma follows from~\eqref{eq:Deps2nktozero} because $K_4 2^{-k} D_\epsilon L$ converges to zero as $k\rightarrow\infty$.
\end{IEEEproof}

% \begin{lemma}\label{lem:epslmlemma}
% Suppose $\sabs{\lambda} < \epsilon$ and $\sabs{\lambda^*} < \epsilon$ with $\epsilon < \tfrac{\pi}{M}$. Then
% \begin{align*}
% d(\lambda, \lambda^*) &= \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda^*) \big)^2 \\
% &\leq R_i^2 L \left( (\lambda - \lambda^*)^2 + 4 C_\epsilon \right).
% \end{align*}
% \end{lemma}

% \begin{lemma}
% If $i \in P$, then $\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 \leq R_i^2(\lambda - \lambda^*)^2.$
% \end{lemma}
% \begin{IEEEproof} 
% We have
% \[
% \big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 = R_i^2\sabs{\sin(\lambda + \Phi_i) - \sin(\lambda^* + \Phi_i)}^2
% \]
% and, since $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
% \[
% \sabs{\sin(\lambda + \Phi_i) - \sin(\lambda^* + \Phi_i)} \leq K\sabs{\lambda - \lambda^*} = \sabs{\lambda - \lambda^*}.
% \]
% \end{IEEEproof}

% \begin{lemma}
% Suppose $\sabs{\lambda} < \epsilon$ and $\sabs{\lambda^*} < \epsilon$ with $\epsilon < \tfrac{\pi}{M}$.  If $i \in D$, then
% \begin{equation}\label{eq:fismall}
% \big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 \leq R_i^2(\lambda - \lambda^*)^2
% \end{equation}
% when $\Phi_i \notin S_\epsilon$, otherwise,
% \begin{equation}\label{eq:fibig}
% \big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 \leq 4 R_i^2.
% \end{equation}
% \end{lemma}
% \begin{IEEEproof}
% Because $\sin(\cdot) \leq 1$ it follows that
% \begin{align*}
% \big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 &= R_i^2\sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\lambda^* + \Phi_i}}^2 \\
% &\leq 4 R_i^2
% \end{align*}
% for any $\Phi_i \in \reals$, and so~\eqref{eq:fibig} holds.  If $\Phi_i \notin S_\epsilon$ then $\Phi_i \in (\psi_{k-1} + \epsilon, \psi_{k} - \epsilon)$ for some $k\in\ints$ and 
% \[
% \fracpart{\Phi_i + \lambda} = \Phi_i + \lambda - \tfrac{2\pi}{M}k
% \] 
% and
% \[
% \fracpart{\Phi_i + \lambda^*} = \Phi_i + \lambda^* - \tfrac{2\pi}{M}k 
% \]
% and, since $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
% \begin{align*}
% \vert \sin&\fracpart{\Phi_i + \lambda} - \sin\fracpart{\Phi_i + \lambda^*}\vert \\
% &=  \sabs{\sin(\Phi_i + \lambda - \tfrac{2\pi}{M}k) - \sin(\Phi_i + \lambda^* - \tfrac{2\pi}{M}k)} \\
% &\leq K \sabs{\lambda - \lambda^*} \\
% &= \sabs{\lambda - \lambda^*}.
% \end{align*}
% Thus~\eqref{eq:fismall} holds. 
% \end{IEEEproof}
